### 2014-10-22 ThesisJo/introduction.tex
End of day.

>>>>

\section{Scattering models}

Defining parameters:
- Roughness
- Incident angle
- Frequency

Reflection and scattering from surfaces:

Roughness >> wavelength:
- Roughness > wavelength: Helmholtz-Kirchhoff (physical optics approach) (Hovem). Leads to Huygins priciple.
- Roughness < wavelength: Rayleigh-Rice (perturbation technique) (Hovem). More accurate at slightly rough surfaces.

Rayleigh. chi = 2 k sigma sin(theta): Rayleigh criterion: Surface is acoustically smooth when chi << 1.
